Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-06 doc/PRF2022/PRF_main.tex
worked on methods a bit

%%%
\subsection{Hydrophobic Attraction Potential Mobility Problem} 
The mathematical formulation is a nonlinear system for the dynamics of a
collection of rigid Janus particles. For the sake of completeness, we
summarize the governing equations here, and a complete description is in
our previous work~\cite{our_paper}. The interactions satisfy a system
of partial differential equations (PDEs) that describe the hydrodynamic
interactions and hydrophobic interactions. Assuming inertial terms are
negligible, the solvent is goverened by the Stokes equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
background flow, and $\mu$ is the constant viscosity. The domain $\Omega
= \Omega(t)$ is the fluid region surrounding the particles and changes
shape as the particles move. Since the particles are rigid, the solvent
velocity satisfies the no-slip rigid body motion boundary condition
\begin{align}
  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity and $\omega_i$ is the
angular velocity. Once these velocities are determined, we use
second-order Adams-Bashforth to update the particle configuration.

The translational and angular velocities guarantee that the fluid forces
balanace the imposed forces. The imposed forces include the hydrophobic
interactions that arise so that particles minimize the free energy of
the structure of the surronding water molecules. The free energy
functional is
\begin{align}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds which is
much smaller than characteristic time for particle motion.
%\cite{MaGa13}. 
Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
conditions on $f(u)$,
% (\cite{evans10}, \S 8.2),
$u$ satisfies the Euler-Lagrange equation
\begin{alignat}{3}
  \label{eq:SL}
  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
  u &= g, && \xx \in \bd\Omega, \\
  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
\end{alignat}
Equation~\eqref{eqn:eq:SL} is solved with a boundary integral equation
method. The boundary condition $g$ is a material label that is
transported with the particle (Figure~\ref{fig:bcs}).

@@

\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
%
where the number of particles $N_b$, the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy

\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
  &&i = 1,\ldots,N_b.
\end{alignat}

>>>>

%%%
\subsection{Hydrophobic Attraction Potential Mobility Problem} 
The mathematical formulation is a nonlinear system for the dynamics of a
collection of rigid Janus particles. For the sake of completeness, we
summarize the governing equations here, and a complete description is in
our previous work~\cite{fu-qua-ryh-you2022}. The interactions satisfy a
system of partial differential equations (PDEs) that describe the
hydrodynamic interactions and hydrophobic interactions. Assuming
inertial terms are negligible, the solvent is goverened by the Stokes
equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
background flow, and $\mu$ is the constant viscosity. The domain $\Omega
= \Omega(t)$ is the fluid region surrounding the particles and changes
shape as the particles move. Since the particles are rigid, the solvent
velocity satisfies the no-slip rigid body motion boundary condition
\begin{align}
  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity and $\omega_i$ is the
angular velocity. Once these velocities are determined, we use
second-order Adams-Bashforth to update the particle configuration.

The translational and angular velocities guarantee that the fluid forces
balanace the imposed forces. The imposed forces include the hydrophobic
interactions that arise so that particles minimize the free energy of
the structure of the surronding water molecules. The free energy
functional is
\begin{align}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds which is
much smaller than characteristic time for particle motion.
%\cite{MaGa13}. 
Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
conditions on $f(u)$,
% (\cite{evans10}, \S 8.2),
$u$ satisfies the Euler-Lagrange equation
\begin{alignat}{3}
  \label{eq:SL}
  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
  u &= g, && \xx \in \bd\Omega, \\
  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
\end{alignat}
Equation~\eqref{eq:SL} is solved with a boundary integral equation
method. The boundary condition $g$ is a material label that is
transported with the particle (Figure~\ref{fig:bcs}).

@@

To solve the Stokes equation with the correct boundary conditions, we
represent the velocity as the of a layer potential with Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
%
Then, the density function $\eeta$, translation velocity $\vv_i$ and
angular velocity $\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
  &&i = 1,\ldots,N_b.
\end{alignat}
